quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-13 paper-quollr.Rmd
Added intro for the visualization

The package provides five basic visualizations which includes one to visualize the full hexagonal grid in $2\text{-}D$, three visualizations related to the $2\text{-}D$ model (static visualizations), and one related to the $p\text{-}D$ model (dynamic visualization). Each visualization can be generated using its respective function, as described in this section.

@@

## Find the most appropriate fit

>>>>

The package offers several $2-\text{D}$ visualizations, including:

- A full hexagonal grid,
- A hexagonal grid that matches the data,
- A full grid based on centroid triangulation,
- A centroid triangulation grid that aligns with the data, 
- A triangular mesh for any provided set of points.

The generated p-D model, overlaid with the data, can also be visualized using `show_langevitour`. Additionally, it features a function for visualizing the $2-\text{D}$ projection of the fitted model overlaid on the data, called `plot_proj`.

Furthermore, there are two interactive plots, `show_link_plots` and `show_error_link_plots`, which are designed to help diagnose the model.

Each visualization can be generated using its respective function, as described in this section.

@@

# Find the most appropriate fit

### 2025-05-13 paper-quollr.tex
Added intro for the visualization

The package provides five basic visualizations which includes one to visualize the full hexagonal grid in \(2\text{-}D\), three visualizations related to the \(2\text{-}D\) model (static visualizations), and one related to the \(p\text{-}D\) model (dynamic visualization). Each visualization can be generated using its respective function, as described in this section.

@@

\subsection{Find the most appropriate fit}\label{find-the-most-appropriate-fit}

>>>>

The package offers several \(2-\text{D}\) visualizations, including:

\begin{itemize}
\tightlist
\item
  A full hexagonal grid,
\item
  A hexagonal grid that matches the data,
\item
  A full grid based on centroid triangulation,
\item
  A centroid triangulation grid that aligns with the data,
\item
  A triangular mesh for any provided set of points.
\end{itemize}

The generated p-D model, overlaid with the data, can also be visualized using \texttt{show\_langevitour}. Additionally, it features a function for visualizing the \(2-\text{D}\) projection of the fitted model overlaid on the data, called \texttt{plot\_proj}.

Furthermore, there are two interactive plots, \texttt{show\_link\_plots} and \texttt{show\_error\_link\_plots}, which are designed to help diagnose the model.

Each visualization can be generated using its respective function, as described in this section.

@@

\section{Find the most appropriate fit}\label{find-the-most-appropriate-fit}
